Short paper : Automatic predicate testing in formal certification

### 2016-02-19 ProofsAndTests/paper-TAP/content/3-testingInside.tex
paper continued
save before change from vect to list

\section{Testing the predicates inside the proof assistant}

@@

>>>>

\section{Testing the predicate by automatic generation of terms}

\label{sect:testingInside}

It is often easier to generate examples of something than it is to precisely define it. Thus, we will define a function that is supposed to generate the lists that we know sorted.

in order to ensure that the predicate captures the notion that we want for \emph{any} term, we write a function that will

@@

- New : a very nice aspect is that we can now automatically generate \emph{all} the terms that satisfy the predicate. it is therefore possible to see some speciffic terms and to check weather they should have been captures or not.
